---
title: "Analyzing Survey Results"
author: "Carl Howe, RStudio"
date: "10/8/2019"
output: html_document
params:
  workshop: "Welcome to the Tidyverse"
  filename: "atl-welcome-tidyverse.csv"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(dplyr)
library(tidyr)
library(ggplot2)
library(DT)
library(flexdashboard)

```

## Import Data 

We can read in the survey data for `r params$workshop` that we just collected using the `googlesheets` package. However, because of challenges associated with the old OAUTH package on the Googlesheets API, I just downloaded the data and am reading it in locally.

```{r import, echo=FALSE, message=FALSE}

responses <- read_csv(params$filename)
names(responses) <- c("timestamp", "day", "session", "overall", "content", "presenters", "recommend", "cloud", "best", "least", "left_out", "comments")
```

We now have the data in a data frame called `responses` and it has `r nrow(responses)` survey responses in it.

## Tidying the Data

Let's look at the data to get a sense of how it is formatted.

```{r tidy, echo=FALSE, message=FALSE}
datatable(responses)
```


## Overall Ratings

```{r visualize, echo=FALSE, message = FALSE, warning = FALSE}
numeric_responses <- responses %>% 
  filter(!is.na(session) & !is.na(day)) %>% 
  select(day:cloud) %>% 
  pivot_longer(overall:cloud, names_to = "name", values_to = "value") %>% 
  mutate(short_session = str_trunc(session, width = 21))

mean_responses <- responses %>%
  summarize(overall = round(mean(overall, na.rm = TRUE), 1),
            content = round(mean(content, na.rm = TRUE), 1),
            presenters = round(mean(presenters, na.rm = TRUE), 1),
            promoters = sum(recommend == 9 | recommend == 10, na.rm=TRUE),
            detractors = sum(recommend %in% 1:6, na.rm = TRUE), 
            recommend = round(mean(recommend, na.rm = TRUE), 1),
            cloud = round(mean(cloud, na.rm = TRUE), 1),
            n = n(),
            nps = round(promoters / n * 100 - detractors / n * 100),
            nps_rating = cut(nps, 
                             breaks = c(-100, 0, 50, 75, 100), 
                             labels = c("Dangerous", "Good", "Excellent", "World Class")))

## Just keeping the numeric values.
mean_responses_long <- mean_responses %>%
  select(overall, content, presenters, recommend, cloud) %>% 
  pivot_longer(overall:cloud, names_to = "name", values_to = "value")

theme_set(theme_minimal())
p <- ggplot(numeric_responses) +
    geom_boxplot(aes(x = name, y = value), fill = "blue", alpha = 0.1, 
                 notch = TRUE, notchwidth = 0.85) +
    geom_point(aes(x = name, y = value), 
               position = "jitter", color = "blue", alpha = 0.2) +
    geom_text(data=mean_responses_long, 
              aes(x = name, 
                  y = 2, 
                  label = paste0("mean=", value)), 
              color = "blue") +
    geom_label(data=mean_responses, aes(label = paste0("Net Promoter Score = ", nps, ", Rating is ", nps_rating)),
               x = Inf, y = 1.5, hjust = 1) +
    scale_y_continuous(breaks = seq(0, 10, 2)) +
    scale_color_brewer(palette = "Set1") +
    theme(axis.text.x = element_text(angle = 45, hjust = 1), legend.position = "bottom") +
    ggtitle(paste0("Overall ", params$workshop, " Numeric Ratings"), subtitle = paste0("N = ", mean_responses$n ))
print(p)
```

## Numeric Ratings By Session

```{r visualize_by_session, echo=FALSE, message=FALSE, warning=FALSE}
numeric_responses <- responses %>% 
  filter(!is.na(session) & !is.na(day)) %>% 
  select(session:cloud) %>% 
  pivot_longer(overall:cloud, names_to = "name", values_to = "value") %>% 
  mutate(short_session = str_trunc(session, width = 21))

mean_responses <- responses %>%
  mutate(short_session = str_trunc(session, width = 21)) %>% 
  group_by(session, short_session) %>% 
  summarize(overall = round(mean(overall, na.rm = TRUE), 1),
            content = round(mean(content, na.rm = TRUE), 1),
            presenters = round(mean(presenters, na.rm = TRUE), 1),
            promoters = sum(recommend == 9 | recommend == 10, na.rm=TRUE),
            detractors = sum(recommend %in% 1:6, na.rm = TRUE), 
            recommend = round(mean(recommend, na.rm = TRUE), 1),
            cloud = round(mean(cloud, na.rm = TRUE), 1),
            n = n(),
            nps = round(promoters / n * 100 - detractors / n * 100),
            nps_rating = cut(nps, 
                             breaks = c(-100, 0, 50, 75, 100), 
                             labels = c("Dangerous", "Good", "Excellent", "World Class")))

## Just keeping the numeric values.
mean_responses_long <- mean_responses %>%
  filter(!is.na(session)) %>% 
  select(session, short_session, overall, content, presenters, recommend, cloud) %>% 
  pivot_longer(overall:cloud, names_to = "name", values_to = "value")

theme_set(theme_minimal())
ggplot(numeric_responses) +
    geom_boxplot(aes(x = name, y = value, color = session, fill = session),
                 alpha = 0.1, notch = TRUE, notchwidth = 0.85) +
    geom_point(aes(x = name, y = value, color = session), 
               position = "jitter", alpha = 0.2) +
    geom_text(data=mean_responses_long, 
              aes(x = name,
                  label = paste0("mean=", value)), 
              y = 1.5, size = 2.5, color = "blue") +
    scale_y_continuous(limits = c(0,10), breaks = seq(0, 10, 2)) +
    scale_color_brewer(palette = "Set1") +
    scale_fill_brewer(palette = "Set1") +
    theme(axis.text.x = element_text(angle = 45, hjust = 1), 
          legend.position = "bottom") +
    guides(color = guide_legend(direction = "vertical"),
           fill = guide_legend(direction = "vertical")) +
    facet_wrap( ~ short_session)
```

## Numeric Ratings By Day

```{r visualize_by_day, echo=FALSE, message=FALSE, warning=FALSE}
numeric_responses <- responses %>% 
  filter(!is.na(session) & !is.na(day)) %>%
  select(day, overall, content, presenters, recommend, cloud) %>% 
  pivot_longer(overall:cloud, names_to = "name", values_to = "value") %>% 
  mutate(short_day = paste0("Day ",str_trunc(day, width = 21)))

mean_responses <- responses %>%
  mutate(short_day = paste0("Day ",str_trunc(day, width = 21))) %>% 
  group_by(day, short_day) %>% 
  summarize(overall = round(mean(overall, na.rm = TRUE), 1),
            content = round(mean(content, na.rm = TRUE), 1),
            presenters = round(mean(presenters, na.rm = TRUE), 1),
            promoters = sum(recommend == 9 | recommend == 10, na.rm=TRUE),
            detractors = sum(recommend %in% 1:6, na.rm = TRUE), 
            recommend = round(mean(recommend, na.rm = TRUE), 1),
            cloud = round(mean(cloud, na.rm = TRUE), 1),
            n = n(),
            nps = round(promoters / n * 100 - detractors / n * 100),
            nps_rating = cut(nps, 
                             breaks = c(-100, 0, 50, 75, 100), 
                             labels = c("Dangerous", "Good", "Excellent", "World Class")))

## Just keeping the numeric values.
mean_responses_long <- mean_responses %>%
  filter(!is.na(day)) %>% 
  select(day, overall, content, presenters, recommend, cloud) %>% 
  pivot_longer(overall:cloud, names_to = "name", values_to = "value")

theme_set(theme_minimal())
ggplot(numeric_responses) +
    geom_boxplot(aes(x = name, y = value, color = short_day, fill = short_day),
                 alpha = 0.1, notch = TRUE, notchwidth = 0.85) +
    geom_point(aes(x = name, y = value, color = short_day), 
               position = "jitter", alpha = 0.2) +
    geom_text(data=mean_responses_long, 
              aes(x = name, label = paste0("mean=", value)), 
              y = 1.5, size = 2.5, color = "blue") +
    scale_y_continuous(limits = c(0,10), breaks = seq(0, 10, 2)) +
    scale_color_brewer(palette = "Set2") +
    scale_fill_brewer(palette = "Set2") +
    theme(axis.text.x = element_text(angle = 45, hjust = 1), 
          legend.position = "bottom") +
    guides(color = guide_legend(direction = "vertical"),
           fill = guide_legend(direction = "vertical")) +
    facet_wrap( ~ short_day)
```



